Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-08-15 noise_covid_v2.Rmd
changes

@@

@@

>>>>

![Fitted Curves With Three Spline Degrees of Freedom](figures/FL_signif_fittedcurves.pdf)

@@

We use a second diagnostic plot, squared residuals versus squared fitted values to look for a linear trend in the Florida counties with a significant LRT test result for the Thanksgiving hypothesis. If the constant dispersion model (NB2) model is ok, then we should see a linear trend. If that checks out, then we don’t have to consider more complicated models.

@@

![Diagnostic Plot 2](figures/diagnostic_plot.2.pdf)
